---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# universe 

<!-- badges: start -->
[![universe status badge](https://ropensci.r-universe.dev/badges/universe)](https://ropensci.r-universe.dev)
[![R-CMD-check](https://github.com/ropensci/universe/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ropensci/universe/actions/workflows/R-CMD-check.yaml)
[![codecov](https://codecov.io/gh/ropensci/universe/branch/main/graph/badge.svg)](https://codecov.io/gh/ropensci/universe)
<!-- badges: end -->

> Tools for Working with [R-universe](https://r-universe.dev) and its APIs.

## Installation and docs

You can install the development version of universe from r-universe:

``` r
install.packages("universe", repos = "https://ropensci.r-universe.dev")
```

Or the development version of universe from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("ropensci/universe")
```

Documentation is available on <https://docs.ropensci.org/universe>.
 
## Enable a repository

Use `runiverse::add()` to opt-in to a package repository (this will modify your `options('repos')` list).

``` r
# Install a package from r-universe
universe::add("ropensci")
install.packages("magick")
```

For more details see the documentation for [runiverse::add()](https://docs.ropensci.org/universe/reference/add.html).


## Get data from the APIs

### All packages in an universe

```{r example}
library(universe)
universe_ls("jeroen")
```

### Info on all packages in an universe

```{r}
universe_all_packages("jeroen", limit = 1) |>
  str(max.level = 2)
```

### Info on a single package in an universe

```{r}
universe_one_package("jeroen", package = "curl") |>
  str(max.level = 1)
```

### Search within a single universe

```{r}
universe_search("ropensci", query = 'needs:httr2', limit = 1) |>
  str(max.level = 2)
```

### Search among all universes

```{r}
global_search(query = '"weather data"', limit = 1) |>
  str(max.level = 2)
```
